---
title: "RWorksheet_montealto#4a"
author: "Pierre Vincent S. Montealto Jr."
date: "2024-10-14"
output: pdf_document
---

1. The table below shows the data about shoe size and height. Create a data frame.

```{r}
ShoeSize <- c(6.5, 9.0, 8.5, 8.5, 10.5, 7.0, 9.5, 9.0, 13.0, 7.5, 10.5, 8.5, 12.0, 10.5, 13.0, 11.15, 8.5, 5.0, 10.0, 6.5, 7.5, 8.5, 10.5, 8.5, 10.5, 11.0, 9.0, 13.0)
Height <- c(66.0, 68.0, 64.5, 65.0, 70.0, 64.0, 70.0, 71.0, 72.0, 64.0, 74.5, 67.0, 71.0, 71.0, 77.0, 72.0, 59.0, 62.0, 72.0, 66.0, 64.0, 67.0, 73.0, 69.0, 72.0, 70.0, 69.0, 70.0)
Gender <- c("F", "F", "F", "F", "M", "F", "F", "F", "M", "F", "M", "F", "M", "M", "M", "M", "F", "F", "M", "F", "F", "M", "M", "F", "M", "M", "M", "M")

ShoeHeightdf <- data.frame(ShoeSize = ShoeSize, Height = Height, Gender = Gender)
ShoeHeightdf

```


a. Describe the data.

-It includes shoe size, height, and gender.





b. Create a subset by males and females with their corresponding shoe size and height. What its result? Show the R scripts.
```{r}
MaleSubset <- subset(ShoeHeightdf, Gender == "M")
FemaleSubset <- subset(ShoeHeightdf, Gender == "F")
MaleSubset
FemaleSubset

```

c. Find the mean of shoe size and height of the respondents. Write the R scripts and its result.
```{r}
meanShoeSize <- mean(ShoeHeightdf$ShoeSize)
meanHeight <- mean(ShoeHeightdf$Height)
print(paste("Mean Shoe Size:", meanShoeSize))
print(paste("Mean Height:", meanHeight))

```

d.Is there a relationship between shoe size and height? Why?

-Yes, there is a strong positive relationship between shoe size and height, with a correlation coefficient of approximately 0.82, indicating that taller individuals tend to have larger shoe sizes.

2. Construct character vector months to a factor with factor() and assign the result to
factor_months_vector. Print out factor_months_vector and assert that R prints out
the factor levels below the actual values.

```{r}
vect_months <- c("March", "April", "January", "November", "January", "September", "October", "September", "November", "August", "January", "November", "November", "February", "May", "August", "July", "December", "August", "August", "September", "November", "February", "April")
factor_months_vector <- factor(vect_months)
factor_months_vector
```


3. Then check the summary() of the months_vector and factor_months_vector. | Inter-
pret the results of both vectors. Are they both equally useful in this case?

```{r}
SummaryM <- summary(vect_months)
SummaryF <- summary(factor_months_vector)
SummaryM
SummaryF
```

4. Create a vector and factor for the table below.


```{r}
Direction <- c("East", "West", "North")
Frequency <- c(1, 4, 3)
directiondf <- data.frame(Direction, Frequency)
direction_order <- factor(Direction, levels = c("East", "West", "North"))
directiondf
direction_order
```

5. Enter the data below in Excel with file name = import_march.csv

a. Import the excel file into the Environment Pane using read.table() function.
Write the code.
 
```{r}
TableReader <- read.table("import_march.csv", header=TRUE, sep=",")
TableReader
```

b. View the dataset. Write the R scripts and its result.

```{r}
print(TableReader)
```






