---
title: "RWorksheet_montealto#4a"
author: "Pierre Vincent S. Montealto Jr."
date: "2024-10-14"
output: pdf_document
---

1. The table below shows the data about shoe size and height. Create a data frame.

```{r}
ShoeSize <- c(6.5, 9.0, 8.5, 8.5, 10.5, 7.0, 9.5, 9.0, 13.0, 7.5, 10.5, 8.5, 12.0, 10.5, 13.0, 11.15, 8.5, 5.0, 10.0, 6.5, 7.5, 8.5, 10.5, 8.5, 10.5, 11.0, 9.0, 13.0)
Height <- c(66.0, 68.0, 64.5, 65.0, 70.0, 64.0, 70.0, 71.0, 72.0, 64.0, 74.5, 67.0, 71.0, 71.0, 77.0, 72.0, 59.0, 62.0, 72.0, 66.0, 64.0, 67.0, 73.0, 69.0, 72.0, 70.0, 69.0, 70.0)
Gender <- c("F", "F", "F", "F", "M", "F", "F", "F", "M", "F", "M", "F", "M", "M", "M", "M", "F", "F", "M", "F", "F", "M", "M", "F", "M", "M", "M", "M")

ShoeHeightdf <- data.frame(ShoeSize = ShoeSize, Height = Height, Gender = Gender)
ShoeHeightdf

```


a. Describe the data.

-It includes shoe size, height, and gender.





b. Create a subset by males and females with their corresponding shoe size and height. What its result? Show the R scripts.
```{r}
MaleSubset <- subset(ShoeHeightdf, Gender == "M")
FemaleSubset <- subset(ShoeHeightdf, Gender == "F")
MaleSubset
FemaleSubset

```

c. Find the mean of shoe size and height of the respondents. Write the R scripts and its result.
```{r}
meanShoeSize <- mean(ShoeHeightdf$ShoeSize)
meanHeight <- mean(ShoeHeightdf$Height)
print(paste("Mean Shoe Size:", meanShoeSize))
print(paste("Mean Height:", meanHeight))

```

d.Is there a relationship between shoe size and height? Why?

-Yes, there is a strong positive relationship between shoe size and height, with a correlation coefficient of approximately 0.82, indicating that taller individuals tend to have larger shoe sizes.

2. Construct character vector months to a factor with factor() and assign the result to
factor_months_vector. Print out factor_months_vector and assert that R prints out
the factor levels below the actual values.

```{r}
vect_months <- c("March", "April", "January", "November", "January", "September", "October", "September", "November", "August", "January", "November", "November", "February", "May", "August", "July", "December", "August", "August", "September", "November", "February", "April")
factor_months_vector <- factor(vect_months)
factor_months_vector
```


3. Then check the summary() of the months_vector and factor_months_vector. | Inter-
pret the results of both vectors. Are they both equally useful in this case?

```{r}
SummaryM <- summary(vect_months)
SummaryF <- summary(factor_months_vector)
SummaryM
SummaryF
```

4. Create a vector and factor for the table below.


```{r}
Direction <- c("East", "West", "North")
Frequency <- c(1, 4, 3)
directiondf <- data.frame(Direction, Frequency)
direction_order <- factor(Direction, levels = c("East", "West", "North"))
directiondf
direction_order
```

5. Enter the data below in Excel with file name = import_march.csv

a. Import the excel file into the Environment Pane using read.table() function.
Write the code.
 
```{r}
TableReader <- read.table("import_march.csv", header=TRUE, sep=",")
TableReader
```

b. View the dataset. Write the R scripts and its result.

```{r}
print(TableReader)
```
6.

a.
```{r}
select_num <- readline(prompt = "Select a number from 1-50: ")
select_num

if(select_num <= 1 || select_num >= 50 ) {
  print("The number selected is beyond the range of 1 to 50.")
} else if(select_num == 20) {
  print("“TRUE")
}else {
  print(paste("The Selected Number is: ", select_num))
}
```

7.

a.

```{r}
min_num <- function(price) {
  bills  <- c(50, 100, 200, 500, 1000)
  count <- 0
  
  for(bill in bills) {
    if(price >= bill) {
      n <- floor(price / bill)
      count <- count + n
      price <- price %% bill 
    }
  }
  return(count)
}

snack_price <- 1350
cat("Minimum numbers of bills needed: ",min_num(snack_price),"\n")
```

8.

a. 

```{r}
scores <- data.frame(
  Names <- c("Annie", "Thea", "Steve", "Hanna"),
  Grade1 <- c(85, 65, 75, 95),
  Grade2 <- c(65, 75, 55, 75),
  Grade3 <- c(85, 90, 80, 100),
  Grade4 <- c(100, 90, 85, 90)
)

print(scores)
```

b.

```{r}
Annie <- (scores$Grade1[1] + scores$Grade2[1] + scores$Grade3[1] + scores$Grade4[1]) / 4
if (Annie > 90) {
  cat("Annie's average grade this semester is", Annie)
}
  Thea <- (scores$Grade1[2] + scores$Grade2[2] + scores$Grade3[2] + scores$Grade4[2]) / 4
if (Thea > 90) {
  cat("Annie's average grade this semester is", Thea)
}
  Steven <- (scores$Grade1[3] + scores$Grade2[3] + scores$Grade3[3] + scores$Grade4[3]) / 4
if (Steven > 90) {
  cat("Annie's average grade this semester is", Steven)
}
  Hanna <- (scores$Grade1[3] + scores$Grade2[3] + scores$Grade3[3] + scores$Grade4[3]) / 4
if (Hanna > 90) {
  cat("Annie's average grade this semester is", Hanna)
}else{
  print("No students exceeds 90")
}
```

c. Without using the mean function, output as follows for the tests in which the average
score was less than 80 out of 4 tests.
Example output: The nth test was difficult.

```{r}
Grade1Average <- sum(scores$Grade1) / 4
if (Grade1Average < 80) {
  cat("The Grade1 test was difficult with an average score of", Grade1Average)
}
Grade2Average <- sum(scores$Grade2) / 4
if (Grade2Average < 80) {
  cat("The Grade1 test was difficult with an average score of", Grade2Average)
}
Grade3Average <- sum(scores$Grade3) / 4
if (Grade3Average < 80) {
  cat("The Grade1 test was difficult with an average score of", Grade3Average)
}
Grade4Average <- sum(scores$Grade4) / 4
if (Grade4Average < 80) {
  cat("The Grade1 test was difficult with an average score of", Grade4Average)
}
```

d. Without using the max function, output as follows for students whose highest score for
a semester exceeds 90 points.
Example Output: Annie’s highest grade this semester is 95.

```{r}
highestOfAnnie <- scores$Grade1[1]
if (scores$Grade2[1] > highestOfAnnie) highestOfAnnie <- scores$Grade2[1]
if (scores$Grade3[1] > highestOfAnnie) highestOfAnnie <- scores$Grade3[1]
if (scores$Grade4[1] > highestOfAnnie) highestOfAnnie <- scores$Grade4[1]
if (highestOfAnnie > 90) {
   cat("Annie's highest grade this semester is", highestOfAnnie,"\n")
}
highestOfThea <- scores$Grade1[2]
if (scores$Grade2[2] > highestOfThea) highestOfThea <- scores$Grade2[2]
if (scores$Grade3[2] >  highestOfThea)  highestOfThea <- scores$Grade3[2]
if (scores$Grade4[2] >  highestOfThea)  highestOfThea <- scores$Grade4[2]
if ( highestOfThea > 90) {
   cat("Thea's highest grade this semester is",  highestOfThea)
}
highestOfSteve <- scores$Grade1[3]
if (scores$Grade2[3] > highestOfSteve) highestOfSteve <- scores$Grade2[3]
if (scores$Grade3[3] > highestOfSteve) highestOfSteve <- scores$Grade3[3]
if (scores$Grade4[3] > highestOfSteve) highestOfSteve <- scores$Grade4[3]
if (highestOfSteve > 90) {
   cat("Steve's highest grade this semester is", highestOfSteve)
}
highestOfHanna <- scores$Grade1[4]
if (scores$Grade2[4] > highestOfHanna) highestOfHanna <- scores$Grade2[4]
if (scores$Grade3[4] > highestOfHanna) highestOfHanna <- scores$Grade3[4]
if (scores$Grade4[4] > highestOfHanna) highestOfHanna <- scores$Grade4[4]
if (highestOfHanna > 90) {
   cat("Hanna's highest grade this semester is", highestOfHanna)
}
```












