1. Create a vector using : operator

a.Sequence from -5 to 5. Write the R code and its output.
Describe its output.
-This creates a sequence of integers starting from -5 to 5 using the : operator.
```{r}
seq1 <- -5:5
seq1

```
b. x <- 1:7. What will be the value of x?
```{r}
x <- 1:7
x

```
2.* Create a vector using seq() function

a.a. seq(1, 3, by=0.2) # specify step size
Write the R script and its output. Describe the output.
```{r}
seq2 <- seq(1, 3, by=0.2)
seq2

```
3. A factory has a census of its workers. There are 50 workers in total. The following
list shows their ages: 34, 28, 22, 36, 27, 18, 52, 39, 42, 29, 35, 31, 27,
22, 37, 34, 19, 20, 57, 49, 50, 37, 46, 25, 17, 37, 43, 53, 41, 51, 35,
24,33, 41, 53, 40, 18, 44, 38, 41, 48, 27, 39, 19, 30, 61, 54, 58, 26,
18.

a. Access 3rd element, what is the value?
```{r}
ages <- c(34, 28, 22, 36, 27, 18, 52, 39, 42, 29, 35, 31, 27, 22, 37, 34, 
          19, 20, 57, 49, 50, 37, 46, 25, 17, 37, 43, 53, 41, 51, 35, 24, 
          33, 41, 53, 40, 18, 44, 38, 41, 48, 27, 39, 19, 30, 61, 54, 58, 26, 18)

ages[3]

```
b. Access 2nd and 4th element, what are the values?
```{r}
ages[c(2, 4)]

```
c. Access all but the 4th and 12th element is not
included. Write the R script and its output.
```{r}
ages[-c(4, 12)]

```
4. *Create a vector x <- c("first"=3, "second"=0, "third"=9). Then named the
vector, names(x).
```{r}
x <- c("first"=3, "second"=0, "third"=9)
names(x)

```
a. Print the results. Then access x[c("first", "third")].
Describe the output.
- It retrieves the values corresponding to the "first" and "third" named elements.
```{r}
x[c("first", "third")]

```
b. Write the code and its output.
CODE:
x[c("first", "third")]

OUTPUT:
first third 
    3     9 
5. Create a sequence x from -3:2.
```{r}
x <- -3:2
x
```
a. Modify 2nd element and change it to 0;

The second element of the sequence is modified to 0.

b. Write the code and its output.
CODE:
x <- -3:2
x[2] <- 0
x

OUTPUT:
[1] -3  0 -1  0  1  2

6. The following data shows the diesel fuel purchased by Mr. Cruz.

a. Create a data frame for month, price per liter (php)
and purchase-quantity (liter). Write the R scripts and
its output.
```{r}
months <- c("Jan", "Feb", "March", "Apr", "May", "June")
price_per_liter <- c(52.50, 57.25, 60.00, 65.00, 74.25, 54.00)
purchase_quantity <- c(25, 30, 40, 50, 10, 45)

fuel_data <- data.frame(months, price_per_liter, purchase_quantity)
fuel_data

```
b. What is the average fuel expenditure of Mr. Cruz from
Jan to June? Note: Use ‘weighted.mean(liter,
purchase)‘. Write the R scripts and its output.
```{r}
weighted.mean(price_per_liter, purchase_quantity)

```
7. R has actually lots of built-in datasets. For example, the rivers data “gives the lengths
(in miles) of 141 “major” rivers in North America, as compiled by the US Geological
Survey”.

a. Type “rivers” in your R console.
>rivers

b. What are the results?
[1]  735  320  325  392  524  450 1459  135  465  600  330  336  280
 [14]  315  870  906  202  329  290 1000  600  505 1450  840 1243  890
 [27]  350  407  286  280  525  720  390  250  327  230  265  850  210
 [40]  630  260  230  360  730  600  306  390  420  291  710  340  217
 [53]  281  352  259  250  470  680  570  350  300  560  900  625  332
 [66] 2348 1171 3710 2315 2533  780  280  410  460  260  255  431  350
 [79]  760  618  338  981 1306  500  696  605  250  411 1054  735  233
 [92]  435  490  310  460  383  375 1270  545  445 1885  380  300  380
[105]  377  425  276  210  800  420  350  360  538 1100 1205  314  237
[118]  610  360  540 1038  424  310  300  444  301  268  620  215  652
[131]  900  525  246  360  529  500  720  270  430  671 1770

c. Write the R scripts and its outputs.
```{r}
data <- c(length(rivers), sum(rivers), mean(rivers), median(rivers), 
          var(rivers), sd(rivers), min(rivers), max(rivers))
data

```
8. The table below gives the 25 most powerful celebrities and their annual pay as ranked
by the editions of Forbes magazine and as listed on the Forbes.com website.

a. Create vectors according to the above table.
Write the R scripts and its output.
```{r}
celebnames <- c("Tom Cruise", "Rolling Stones", "Oprah Winfrey", "U2", "Tiger Woods", "Steven Spielberg", "Howard Stern", "50 Cent", "Cast of the Sopranos", "Dan Brown", "Bruce Springsteen",  "Donald Trump", "Muhammad Ali", "Paul McCartney", "George Lucas", "Elton John","David Letterman", "Phil Mickelson", "J.K Rowling","Brad Pitt","Peter Jackson","Dr. Phil McGraw", "Jay Lenon", "Celine Dion", "Kobe Bryant")
pay <- c(67, 90, 225, 110, 90, 332, 302, 41, 52, 88, 55, 44, 55, 40, 233, 34, 40, 47, 75, 25, 39, 45, 32, 40, 31)
powerrank <- 1:25
celebdata <- data.frame(PowerRanking = powerrank, CelebrityName = celebnames, Pay = pay)
celebdata
```
b. Modify the power ranking and pay of J.K. Rowling.
Change power ranking to 15 and pay to 90. Write the
R scripts and its output.
```{r}
powerrank[4] <- 15
pay[4] <- 90
powerrank
pay
```
c. Create an excel file from the table above and save it
as csv file(PowerRanking). Import the csv file into
the RStudio. What is the R script?
```{r}
write.csv(celebdata, "Power-Ranking.csv", row.names = FALSE)
datarank <- read.csv("Power-Ranking.csv")
datarank

```


d. Access the rows 10 to 20 and save it as Ranks.RData.
Write the R script and its output.
```{r}
ranksubset <-datarank[10:20, ]
save(ranksubset, file = "Ranks.RData")
```

e. Describe its output.

9. Download the Hotels-Vienna https://tinyurl.com/Hotels-Vienna

a. Import the excel file into your RStudio.
What is the R scrip, 6)
```



10. Create a list of ten (10) vegetables you ate during your lifetime. If none, just list down.

a. Write the R scripts and its output.
CODE:
```{r}
vegetables <- c("Carrot", "Broccoli", "Spinach", "Kale", "Cauliflower", "Tomato", "Cucumber", "Bell Pepper", "Onion", "Lettuce")
vegetables
```
OUTPUT:
 [1] "Carrot"      "Broccoli"    "Spinach"     "Kale"       
 [5] "Cauliflower" "Tomato"      "Cucumber"    "Bell Pepper"
 [9] "Onion"       "Lettuce"  
 
 b. Add 2 additional vegetables after the last vegetables
in the list. What is the R script and its output?
CODE:
```{r}
vegetables <- c(vegetables, "Zucchini", "Eggplant")
vegetables

```
OUTPUT:
[1] "Carrot"      "Broccoli"    "Spinach"     "Kale"       
 [5] "Cauliflower" "Tomato"      "Cucumber"    "Bell Pepper"
 [9] "Onion"   
 
 c. Add 4 additional vegetables after index 5. How many
datapoints does your vegetable list have? What is the
R script and its output?
CODE:
```{r}
vegetables <- append(vegetables, c("Radish", "Pumpkin", "Sweet Potato", "Beetroot"), after = 5)
vegetables
```
OUTPUT:
[1] "Carrot"       "Broccoli"     "Spinach"     
 [4] "Kale"         "Cauliflower"  "Radish"      
 [7] "Pumpkin"      "Sweet Potato" "Beetroot"    
[10] "Tomato"       "Cucumber"     "Bell Pepper" 
[13] "Onion"        "Lettuce"      "Zucchini"    
[16] "Eggplant"   

d. Remove the vegetables in index 5, 10, and 15. How
many vegetables were left? Write the codes and its
output.

CODE:
```{r}
vegetables <- vegetables[-c(5, 10, 15)]
vegetables

```
OUTPUT:
 [1] "Carrot"       "Broccoli"     "Spinach"     
 [4] "Kale"         "Radish"       "Pumpkin"     
 [7] "Sweet Potato" "Beetroot"     "Cucumber"    
[10] "Bell Pepper"  "Onion"        "Lettuce"     
[13] "Eggplant"   
























