1. Create a vector using : operator

a.
-This creates a sequence of integers starting from -5 to 5 using the : operator.

```{r}
seq1 <- -5:5
seq1

```
b. 

```{r}
x <- 1:7
x

```
2.* Create a vector using seq() function

a.

```{r}
seq2 <- seq(1, 3, by=0.2)
seq2

```

3.

a.

```{r}
ages <- c(34, 28, 22, 36, 27, 18, 52, 39, 42, 29, 35, 31, 27, 22, 37, 34, 
          19, 20, 57, 49, 50, 37, 46, 25, 17, 37, 43, 53, 41, 51, 35, 24, 
          33, 41, 53, 40, 18, 44, 38, 41, 48, 27, 39, 19, 30, 61, 54, 58, 26, 18)

ages[3]

```
b.

```{r}
ages[c(2, 4)]

```
c. 

```{r}
ages[-c(4, 12)]

```
4.

```{r}
x <- c("first"=3, "second"=0, "third"=9)
names(x)

```
a.

- It retrieves the values corresponding to the "first" and "third" named elements.

```{r}
x[c("first", "third")]

```
b.

CODE:
x[c("first", "third")]

OUTPUT:
first third 
    3     9 


5. 

```{r}
x <- -3:2
x
```
a. Modify 2nd element and change it to 0;

The second element of the sequence is modified to 0.

b. Write the code and its output.

CODE:
x <- -3:2
x[2] <- 0
x

OUTPUT:
[1] -3  0 -1  0  1  2

6.

a.

```{r}
months <- c("Jan", "Feb", "March", "Apr", "May", "June")
price_per_liter <- c(52.50, 57.25, 60.00, 65.00, 74.25, 54.00)
purchase_quantity <- c(25, 30, 40, 50, 10, 45)

fuel_data <- data.frame(months, price_per_liter, purchase_quantity)
fuel_data

```
b.

```{r}
weighted.mean(price_per_liter, purchase_quantity)

```
7.

a.
>rivers

b. What are the results?

[1]  735  320  325  392  524  450 1459  135  465  600  330  336  280
 [14]  315  870  906  202  329  290 1000  600  505 1450  840 1243  890
 [27]  350  407  286  280  525  720  390  250  327  230  265  850  210
 [40]  630  260  230  360  730  600  306  390  420  291  710  340  217
 [53]  281  352  259  250  470  680  570  350  300  560  900  625  332
 [66] 2348 1171 3710 2315 2533  780  280  410  460  260  255  431  350
 [79]  760  618  338  981 1306  500  696  605  250  411 1054  735  233
 [92]  435  490  310  460  383  375 1270  545  445 1885  380  300  380
[105]  377  425  276  210  800  420  350  360  538 1100 1205  314  237
[118]  610  360  540 1038  424  310  300  444  301  268  620  215  652
[131]  900  525  246  360  529  500  720  270  430  671 1770

c. 

```{r}
data <- c(length(rivers), sum(rivers), mean(rivers), median(rivers), 
          var(rivers), sd(rivers), min(rivers), max(rivers))
data

```
8.

a.

```{r}
celebnames <- c("Tom Cruise", "Rolling Stones", "Oprah Winfrey", "U2", "Tiger Woods", "Steven Spielberg", "Howard Stern", "50 Cent", "Cast of the Sopranos", "Dan Brown", "Bruce Springsteen",  "Donald Trump", "Muhammad Ali", "Paul McCartney", "George Lucas", "Elton John","David Letterman", "Phil Mickelson", "J.K Rowling","Brad Pitt","Peter Jackson","Dr. Phil McGraw", "Jay Lenon", "Celine Dion", "Kobe Bryant")
pay <- c(67, 90, 225, 110, 90, 332, 302, 41, 52, 88, 55, 44, 55, 40, 233, 34, 40, 47, 75, 25, 39, 45, 32, 40, 31)
powerrank <- 1:25
celebdata <- data.frame(PowerRanking = powerrank, CelebrityName = celebnames, Pay = pay)
celebdata
```
b.

```{r}
powerrank[4] <- 15
pay[4] <- 90
powerrank
pay
```
c.

```{r}
write.csv(celebdata, "Power-Ranking.csv", row.names = FALSE)
datarank <- read.csv("Power-Ranking.csv")
datarank

```


d. 

```{r}
ranksubset <-datarank[10:20, ]
save(ranksubset, file = "Ranks.RData")
```


9.

a.

```{r}
library("openxlsx")
library("readxl")
datahotel <- read.xlsx("hotels-vienna.xlsx")
datahotel
```

b.

```{r}
dim(datahotel)
```

c.

```{r}
dataselected <- datahotel[,    c("country", "neighbourhood", "price", "stars", "accommodation_type", "rating")]
dataselected
```

d. 

```{r}
save(dataselected, file ="new.RData")
load("new.RData")
head(dataselected)
tail(dataselected)
```

e. 

```{r}
load("new.RData")
head(dataselected)
tail(dataselected)
```




10.

a. 

CODE:

```{r}
vegetables <- c("Carrot", "Broccoli", "Spinach", "Kale", "Cauliflower", "Tomato", "Cucumber", "Bell Pepper", "Onion", "Lettuce")
vegetables
```
OUTPUT:
 [1] "Carrot"      "Broccoli"    "Spinach"     "Kale"       
 [5] "Cauliflower" "Tomato"      "Cucumber"    "Bell Pepper"
 [9] "Onion"       "Lettuce"  
 

b.

```{r}
vegetables <- c(vegetables, "Zucchini", "Eggplant")
vegetables

```

OUTPUT:
[1] "Carrot"      "Broccoli"    "Spinach"     "Kale"       
 [5] "Cauliflower" "Tomato"      "Cucumber"    "Bell Pepper"
 [9] "Onion"   
 
 c.
 
CODE:

```{r}
vegetables <- append(vegetables, c("Radish", "Pumpkin", "Sweet Potato", "Beetroot"), after = 5)
vegetables
```
OUTPUT:
[1] "Carrot"       "Broccoli"     "Spinach"     
 [4] "Kale"         "Cauliflower"  "Radish"      
 [7] "Pumpkin"      "Sweet Potato" "Beetroot"    
[10] "Tomato"       "Cucumber"     "Bell Pepper" 
[13] "Onion"        "Lettuce"      "Zucchini"    
[16] "Eggplant"   

d.

CODE:

```{r}
vegetables <- vegetables[-c(5, 10, 15)]
vegetables

```
OUTPUT:
 [1] "Carrot"       "Broccoli"     "Spinach"     
 [4] "Kale"         "Radish"       "Pumpkin"     
 [7] "Sweet Potato" "Beetroot"     "Cucumber"    
[10] "Bell Pepper"  "Onion"        "Lettuce"     
[13] "Eggplant"   
























