---
title: "RWorksheet_montealto#4c"
author: "Pierre Vincent S. Montealto Jr."
date: "2024-11-04"
output: pdf_document
---

1. Use the dataset mpg


a. Show your solutions on how to import a csv file into the environment.

```{r}
data_mpg <- read.csv("mpg.csv")
data_mpg
```

b. Which variables from mpg dataset are categorical?

 -The categorical variables are manufacturer, model, trans, drv, fl, class


c. Which are continuous variables?

-The continuous variables are displ, year, cyl, cty, hwy


2. Which manufacturer has the most models in this data set? Which model has the most variations?
Show your answer.

```{r}
library(dplyr)

model_count <- data_mpg %>%
  group_by(manufacturer) %>%
  summarise(model_count = n_distinct(model)) %>%
  arrange(desc(model_count))

top_manufacturer <- model_count[1, ]
top_manufacturer

```

a. Group the manufacturers and find the unique models. Show your codes and result.

```{r}
library(dplyr)

unique_manufacturer_models <- data_mpg %>%
  group_by(manufacturer) %>%
  summarise(unique_model_count = n_distinct(model)) %>%
  arrange(desc(unique_model_count))

unique_manufacturer_models

```
b. Graph the result by using plot() and ggplot(). Write the codes and its result.

```{r}
barplot(unique_manufacturer_models$unique_model_count,
        names.arg = unique_manufacturer_models$manufacturer,
        main = "Number of Unique Models by Manufacturer",
        xlab = "Manufacturer",
        ylab = "Unique Model Count",
        las = 2,        
        col = "skyblue") 

```

```{r}
library(ggplot2)

ggplot(unique_manufacturer_models, aes(x = reorder(manufacturer, -unique_model_count), y = unique_model_count)) +
  geom_bar(stat = "identity", fill = "skyblue") +
  labs(title = "Number of Unique Models by Manufacturer", x = "Manufacturer", y = "Unique Model Count") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))

```

2. Same dataset will be used. You are going to show the relationship of the modeland the manufacturer.

a. What does ggplot(mpg, aes(model, manufacturer)) + geom_point() show?

```{r}
ggplot(mpg, aes(model, manufacturer)) + geom_point()

```

b. For you, is it useful? If not, how could you modify the data to make it more informative?

-For me in its current form is not very useful. The plot only shows each combination of model and manufacturer as a point, but with so many categorical variables and repeated values.

```{r}
library(dplyr)
library(ggplot2)

model_manufacturer_count <- mpg %>%
  group_by(manufacturer, model) %>%
  summarise(count = n()) %>%
  ungroup()

ggplot(model_manufacturer_count, aes(x = model, y = manufacturer, size = count)) +
  geom_point(alpha = 0.7) +
  labs(title = "Model-Manufacturer Relationship", x = "Model", y = "Manufacturer", size = "Count") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))

```


3. Plot the model and the year using ggplot(). Use only the top 20 observations. Write the codes and
its results.

```{r}
library(ggplot2)

top_20 <- mpg[1:20, ]

ggplot(top_20, aes(x = model, y = year)) +
  geom_point(color = "blue", size = 3) +
  labs(title = "Model vs Year (Top 20 Observations)", x = "Model", y = "Year") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))

```



4. Using the pipe (%>%), group the model and get the number of cars per model. Show codes and its result

```{r}
library(dplyr)

cars_per_model <- mpg %>%
  group_by(model) %>%
  summarise(car_count = n()) %>%
  arrange(desc(car_count))

cars_per_model

```


a. Plot using geom_bar() using the top 20 observations only. The graphs shoudl have a title, labels and
colors. Show code and results.

```{r}
library(dplyr)
library(ggplot2)

top_20 <- mpg %>%
  group_by(model) %>%
  summarise(car_count = n()) %>%
  arrange(desc(car_count)) %>%
  slice_head(n = 20)

ggplot(top_20, aes(x = reorder(model, -car_count), y = car_count)) +
  geom_bar(stat = "identity", fill = "skyblue", color = "black") +
  labs(title = "Top 20 Car Models by Count", x = "Model", y = "Number of Cars") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))


```



b. Plot using the geom_bar() + coord_flip() just like what is shown below. Show codes and its result.

```{r}
library(dplyr)
library(ggplot2)

top_20 <- mpg %>%
  group_by(model) %>%
  summarise(car_count = n()) %>%
  arrange(desc(car_count)) %>%
  slice_head(n = 20)

ggplot(top_20, aes(x = reorder(model, car_count), y = car_count)) +
  geom_bar(stat = "identity", fill = "skyblue", color = "black") +
  coord_flip() +
  labs(title = "Top 20 Car Models by Count", x = "Model", y = "Number of Cars") +
  theme_minimal()

```


5. Plot the relationship between cyl - number of cylinders and displ - engine displacement using
geom_point with aesthetic color = engine displacement. Title should be “Relationship between
No. of Cylinders and Engine Displacement”.




a. How would you describe its relationship? Show the codes and its result.

```{r}
library(ggplot2)

ggplot(mpg, aes(x = cyl, y = displ, color = displ)) +
  geom_point(size = 3) +
  labs(title = "Relationship between No. of Cylinders and Engine Displacement",
       x = "Number of Cylinders",
       y = "Engine Displacement (L)") +
  scale_color_continuous(name = "Engine Displacement") +
  theme_minimal()

```

6. Plot the relationship between displ (engine displacement) and hwy(highway miles per gallon). Mapped
it with a continuous variable you have identified in #1-c. What is its result? Why it produced such
output?

```{r}
library(ggplot2)

ggplot(data = mpg, aes(x = displ, y = hwy, color = cty)) +
  geom_point() +
  labs(title = "Relationship between Engine Displacement and Highway MPG",
       x = "Engine Displacement (L)",
       y = "Highway Miles per Gallon",
       color = "City MPG") +
  theme_minimal()

```
- The plot produced such an output due to the inverse relationship between engine displacement  and fuel efficiency metrics.


6. Import the traffic.csv onto your R environment.



a. How many numbers of observation does it have? What are the variables of the traffic dataset the Show
your answer.

```{r}
traffic_data <- read.csv("traffic.csv")

observations <- nrow(traffic_data)
vari <- colnames(traffic_data)

observations
vari

```


b. subset the traffic dataset into junctions. What is the R codes and its output?

```{r}
library(dplyr)


junction_data <- traffic_data %>%
  filter(!is.na(Junction))  

junction_data

```



c. Plot each junction in a using geom_line(). Show your solution and output.

```{r}
library(dplyr)
library(ggplot2)

ggplot(data = traffic_data, aes(x = DateTime, y = Vehicles, color = Junction)) +
  geom_line() +
  labs(title = "Vehicle Counts at Each Junction Over Time",
       x = "DateTime",
       y = "Number of Vehicles",
       color = "Junction") +
  theme_minimal()

```


7. From alexa_file.xlsx, import it to your environment

```{r}
library(readxl)

alexa_data <- read_excel("alexa_file.xlsx")

```


a. How many observations does alexa_file has? What about the number of columns? Show your solution
and answer.

```{r}
num_obser <- nrow(alexa_data)
num_columns <- ncol(alexa_data)

num_obser
num_columns

```


b. group the variations and get the total of each variations. Use dplyr package. Show solution and
answer.

```{r}
library(dplyr)

total_varia <- alexa_data %>%
  group_by(variation) %>%
  summarise(total = n())

total_varia

```


c. Plot the variations using the ggplot() function. What did you observe? Complete the details of the
graph. Show solution and answer.

```{r}
library(ggplot2)

ggplot(total_varia, aes(x = reorder(variation, -total), y = total)) +
  geom_bar(stat = "identity", fill = "skyblue", color = "black") +
  labs(title = "Total Count of Each Variation",
       x = "Variation",
       y = "Total Count") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))

```


d. Plot a geom_line() with the date and the number of verified reviews. Complete the details of the
graphs. Show your answer and solution.

```{r}
ggplot(alexa_data, aes(x = date, y = verified_reviews)) +
  geom_line(color = "blue") +
  labs(title = "Number of Verified Reviews Over Time",
       x = "Date",
       y = "Number of Verified Reviews") +
  theme_minimal()


```



e. Get the relationship of variations and ratings. Which variations got the most highest in rating? Plot a
graph to show its relationship. Show your solution and answer.

```{r}
library(dplyr)
library(ggplot2)

variation_ratings <- alexa_data %>%
  group_by(variation) %>%
  summarise(avg_rating = mean(rating, na.rm = TRUE))

highest_rated_variation <- variation_ratings %>%
  filter(avg_rating == max(avg_rating))

highest_rated_variation

ggplot(variation_ratings, aes(x = reorder(variation, -avg_rating), y = avg_rating)) +
  geom_bar(stat = "identity", fill = "skyblue", color = "black") +
  labs(title = "Average Rating by Variation",
       x = "Variation",
       y = "Average Rating") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))

```


