---
title: "RWorksheet_montealto#4b"
author: "Pierre Vincent S. Montealto Jr."
date: "2024-10-28"
output: pdf_document
---

1. Using the for loop, create an R script that will display a 5x5 matrix as shown in
Figure 1. It must contain vectorA = [1,2,3,4,5] and a 5 x 5 zero matrix.

Hint Use abs() function to get the absolute value

```{r}
vectorA <- 1:5
matrixA <- matrix(0, nrow = 5, ncol = 5)

for (i in 1:5) {
  matrixA[i,] <- abs(vectorA - i)
}

print(matrixA)

```

2.Print the string "*" using for() function. The output should be the same as shown in Figure

```{r}
for (i in 1:5) {
  print(strrep("*", i))
}

```

3.Get an input from the user to print the Fibonacci sequence starting from the 1st input
up to 500. Use repeat and break statements. Write the R Scripts and its output.

```{r}
fibo <- function(n) {
  a <- 0
  b <- 1
  repeat {
    cat(a, " ")
    temp <- a + b
    a <- b
    b <- temp
    if (a > 500) break
  }
}

fibo(500)

```

4. Import the dataset as shown in Figure 1 you have created previously.

a. What is the R script for importing an excel or a csv file? Display the first 6 rows of
the dataset? Show your codes and its result

```{r}
data <- read.csv("Shoesize.csv")

head(data)

```
b.Create a subset for gender(female and male). How many observations are there in
Male? How about in Female? Write the R scripts and its output.

```{r}
males <- subset(data, Gender == "M")
females <- subset(data, Gender == "F")

cat("Number of males:", nrow(males), "\n")
cat("Number of females:", nrow(females), "\n")

```

c. Create a graph for the number of males and females for Household Data. Use plot(),
chart type = barplot. Make sure to place title, legends, and colors. Write the R scripts and
its result.

```{r}
counts <- table(data$Gender)
barplot(counts, main = "Gender Distribution", col = c("blue", "pink"), 
        legend = rownames(counts))

```

5.The monthly income of Dela Cruz family was spent on the following:

a. Create a piechart that will include labels in percentage.Add some colors and title of the chart. Write the R scripts and show its output.

```{r}
expenses <- c(Food = 60, Electricity = 10, Savings = 5, Miscellaneous = 25)

pie(expenses, main = "Dela Cruz Family Monthly Expenses", 
    col = rainbow(length(expenses)), labels = paste(names(expenses), "\n", expenses, "%"))

```
6. Use the iris dataset.

```{r}
data(iris)
```


a.Check for the structure of the dataset using the str() function. Describe what you
have seen in the output.

```{r}
data(iris)
str(iris)

```
b. Create an R object that will contain the mean of the sepal.length,
sepal.width,petal.length,and petal.width. What is the R script and its result?

```{r}
mean_values <- colMeans(iris[, 1:4])
print(mean_values)

```

c. Create a pie chart for the Species distribution. Add title, legends, and colors. Write
the R script and its result.

```{r}
species_counts <- table(iris$Species)
pie(species_counts, main = "Iris Species Distribution", col = c("red", "green", "blue"))

```

d. Subset the species into setosa, versicolor, and virginica. Write the R scripts
and show the last six (6) rows of each species.

```{r}
setosa <- subset(iris, Species == "setosa")
versicolor <- subset(iris, Species == "versicolor")
virginica <- subset(iris, Species == "virginica")

tail(setosa)
tail(versicolor)
tail(virginica)

```


e. Create a scatterplot of the sepal.length and sepal.width using the different
species(setosa,versicolor,virginica). Add a title = “Iris Dataset”, subtitle = “Sepal
width and length, labels for the x and y axis, the pch symbol and colors should be based on
the species.

```{r}
plot(iris$Sepal.Length, iris$Sepal.Width, 
     col = as.numeric(iris$Species), 
     pch = 16, 
     main = "Iris Dataset", 
     sub = "Sepal width and length", 
     xlab = "Sepal Length", ylab = "Sepal Width")
legend("topright", legend = levels(iris$Species), col = 1:3, pch = 16)

```

f. Interpret the result.

-The result is that this plot helps in visualizing the differences in sepal dimensions across the three species of irises and aids in understanding how these species can be differentiated based on their morphological characteristics.


7. Import the alexa-file.xlsx. Check on the variations. Notice that there are extra whitespaces among black variants (Black Dot, Black Plus, Black Show, Black Spot). Also on the white variants (White Dot, White Plus, White Show, White
Spot).








